---
title: "Teaching Analytics"
author: "ROUX Dorian"
output: html_document
---

**Packages**
```{r}
#Import the Libraries.
library('readr')
library('dplyr')
library("tidyr")
library("RColorBrewer")
library('TraMineR')
library('ggplot2')
```

**DataFrame Import**
```{r}
#Import the DataFrame.
prep_Sequences <- select(read_csv(file ='../Data/Quizzes.csv'), -c(1)) #Import the required CSV and Remove the first column that represents the index.
head(prep_Sequences, 10) #Display the ten first rows.
```


**Prepare the Variables**

*Sequences Computer Science Module2 Chapter1* 
```{r}
#Sequences Computer Science Module2 Chapter1
prep_Sequences_mod2chap1 <- prep_Sequences %>% filter(Departement == "Informatique" & Module_ID == 2 & Chapter_ID == 1)

#Reorder the Quizzes ID
prep_Sequences_mod2chap1$Quizz_ID <- replace(prep_Sequences_mod2chap1$Quizz_ID, prep_Sequences_mod2chap1$Quizz_ID>=0, prep_Sequences_mod2chap1$Quizz_ID - prep_Sequences_mod2chap1$Quizz_ID[1] + 1)

#Built the Sequences for the Predict/Real Difficulty of each Quiz of the specific Chapter.
prep_Sequences_mod2chap1_DS <- prep_Sequences_mod2chap1 %>% select(Quizz_ID, Year, Chapter_ID, Difficulty_String) #Select the useful columns.
seq_Sequences_mod2chap1_DS <- spread(prep_Sequences_mod2chap1_DS, Quizz_ID, Difficulty_String) #Spread the values from one column into columns.
mvad.Sequences_mod2chap1_DS <- seqdef(seq_Sequences_mod2chap1_DS[, -c(1:2)]) #Transform the new columns into sequences.

#Set the color and order
seqplot_color = c("#FF0000", "#000FFF", "#F4EFD7", "#FF7878", "#7878FF") #Color of the figure.
legend_color = c('#FF0000', '#FF7878', '#F4EFD7', '#7878FF', '#000FFF') #Color of the legend.
legend_order = c('Beaucoup plus Difficile', 'Plus Difficile', 'Meme Difficulté', 'Plus Facile', 'Beaucoup plus Facile') #Order of the legend.

```


*Sequences Computer Science Module3 Chapter2* 
```{r}
#Sequences Computer Science Module3 Chapter2
prep_Sequences_mod3chap2 <- prep_Sequences %>% filter(Departement == "Informatique" & Module_ID == 3 & Chapter_ID == 2)

#Reorder the Quizzes ID
prep_Sequences_mod3chap2$Quizz_ID <- replace(prep_Sequences_mod3chap2$Quizz_ID, prep_Sequences_mod3chap2$Quizz_ID>=0, prep_Sequences_mod3chap2$Quizz_ID - prep_Sequences_mod3chap2$Quizz_ID[1] + 1)
```

#############################################################
#Build the Sequences and Parameters for the Type of Quizzes #
#############################################################
```{r}
#Built the Sequences for the Type of Quizzes

#Sequences
prep_Sequences_mod3chap2_Type <- prep_Sequences_mod3chap2 %>% select(Quizz_ID, Year, Chapter_ID, Quizz_Type) #Select the useful columns.
seq_Sequences_mod3chap2_Type <- spread(prep_Sequences_mod3chap2_Type, Quizz_ID, Quizz_Type) #Spread the values from one column into columns.
mvad.Sequences_mod3chap2_Type <- seqdef(seq_Sequences_mod3chap2_Type[, -c(1:2)]) #Transform the created columns into sequences.

#Colors/Order
seqplot_color_Type = c('#FFFF00', '#FFD740', '#64FFDA', '#69F0AE') #Color of the Figure.
legend_color_Type = c('#FFD740', '#FFFF00', '#69F0AE', '#64FFDA') #Color of the Legend.
legend_order_Type = c('QCU', 'QCM', 'QROC', 'QO') #Order of the Legend.
```

##################################################################
#Build the Sequences and Parameters for the Predicted Difficulty #
##################################################################
```{r}
#Built the Sequences for the Predicted Difficulty

#Sequences
prep_Sequences_mod3chap2_Predicted <- prep_Sequences_mod3chap2 %>% select(Quizz_ID, Year, Chapter_ID, Predict_Difficulty) #Select the useful columns.
seq_Sequences_mod3chap2_Predicted<- spread(prep_Sequences_mod3chap2_Predicted, Quizz_ID, Predict_Difficulty) #Spread the values from one column into columns.
mvad.Sequences_mod3chap2_Predicted <- seqdef(seq_Sequences_mod3chap2_Predicted[, -c(1:2)]) #Transform the created columns into sequences.

#Colors/Order
seqplot_color_Predicted = c('#FF5722', '#4FC3F7', '#81C784') #Color of the Figure.
legend_color_Predicted = c('#4FC3F7', '#81C784', '#FF5722') #Color of the Legend.
legend_order_Predicted =  c('Facile', 'Moyen', 'Difficile') #Order of the Legend.
```

#############################################################
#Build the Sequences and Parameters for the Real Difficulty #
#############################################################
```{r}
#Built the Sequences for the Real Difficulty

#Sequences
prep_Sequences_mod3chap2_Real <- prep_Sequences_mod3chap2 %>% select(Quizz_ID, Year, Chapter_ID, Correct_Difficulty) #Select the useful columns.
seq_Sequences_mod3chap2_Real <- spread(prep_Sequences_mod3chap2_Real, Quizz_ID, Correct_Difficulty) #Spread the values from one column into columns.
mvad.Sequences_mod3chap2_Real <- seqdef(seq_Sequences_mod3chap2_Real[, -c(1:2)]) #Transform the created columns into sequences.

#Colors/Order
seqplot_color_Real = c('#FF5722', '#4FC3F7', '#81C784') #Color of the Figure.
legend_color_Real = c('#4FC3F7', '#81C784', '#FF5722') #Color of the Legend.
legend_order_Real =  c('Facile', 'Moyen', 'Difficile') #Order of the Legend.
```

#######################################################################
#Build the Sequences and Parameters for the Predicted/Real Difficulty #
#######################################################################
```{r}
#Built the Sequences and Parameters for the Predicted/Real Difficulty

#Sequences
prep_Sequences_mod3chap2_PR <- prep_Sequences_mod3chap2 %>% select(Quizz_ID, Year, Chapter_ID, Difficulty_String) #Select the useful columns.
seq_Sequences_mod3chap2_PR <- spread(prep_Sequences_mod3chap2_PR, Quizz_ID, Difficulty_String) #Spread the values from one column into columns.
mvad.Sequences_mod3chap2_PR <- seqdef(seq_Sequences_mod3chap2_PR[, -c(1:2)]) #Transform the created columns into sequences.

#Colors/Order
seqplot_color_PR = c("#FF0000", "#000FFF", "#F4EFD7", "#FF7878", "#7878FF") #Color of the Figure.
legend_color_PR = c("#FF0000", "#FF7878", "#F4EFD7", "#7878FF", "#000FFF") #Color of the Legend.
legend_order_PR = c("Beaucoup plus Difficile", "Plus Difficile", "Meme Difficulté", "Plus Facile", "Beaucoup plus Facile") #Order of the Legend.
```

################################################################
#Build the Sequences and Parameters for the Adapted Difficulty #
################################################################
```{r}
#Built the Sequences for the Adapted Difficulty

#Sequences
prep_Sequences_mod3chap2_Adapted <- prep_Sequences_mod3chap2 %>% select(Quizz_ID, Year, Chapter_ID, Difficulty) #Select the useful columns.
seq_Sequences_mod3chap2_Adapted <- spread(prep_Sequences_mod3chap2_Adapted, Quizz_ID, Difficulty) #Spread the values from one column into columns.
mvad.Sequences_mod3chap2_Adapted <- seqdef(seq_Sequences_mod3chap2_Adapted[, -c(1:2)]) #Transform the created columns into sequences.

#Colors/Order
seqplot_color_Adapted = c('#FFE0B2', '#FF5722') #Color of the Figure.
legend_color_Adapted = c('#FFE0B2', '#FF5722') #Color of the Legend.
legend_order_Adapted = c('Quiz Adapté', 'Quiz Non-Adapté') #Order of the Legend.
```


**Prepare the Figures**

###################################################
#Build the Figure of the Predicted/RealDifficulty #
###################################################
```{r}
#Figure of the Predicted/Real Difficulty

#Define the name of the file
fig_Sequences_mod3chap2_PR = paste("Seq-PR-Chap_", unique(prep_Sequences_mod3chap2$Chapter_ID),
                                   "-Mod_", unique(prep_Sequences_mod3chap2$Module_ID),
                                   "-Dep_", unique(prep_Sequences_mod3chap2$Departement), "-2015_2020", sep = "")

#Set the Figure file name and Figure size, margins and positions of the graphs
png(paste("../Figures/", fig_Sequences_mod3chap2_PR, ".png", sep = ""), heigh = 800, width = 1300)
layout(matrix(c(1, 1, 1, 1, 2, 2), ncol=6, byrow=TRUE))
par(mar=c(9,9,3,0)+0.1, oma=c(0,1,9,0))

#Define the title of the Figure
title_Sequences_mod3chap2_PR = paste(
  "Séquences de la Différence entre la Difficulté Prédite par rapport à la Difficulté Réelle de 2015 à 2020, \n",
  "de chaque Quiz du chapitre", paste("«", unique(prep_Sequences_mod3chap2$Chapter), "»,", sep = ""), 
  "du module", paste("«", unique(prep_Sequences_mod3chap2$Module), "»,", sep = ""),
  "du Département", paste("d'", unique(prep_Sequences_mod3chap2$Departement), ".", sep = ""))

#Plot the Seqplot Predicted/Real Difficulty and Define its axis and labels
seqplot(mvad.Sequences_mod3chap2_PR, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_mod3chap2_PR)),
        cpal = seqplot_color_PR, space = 0.15, main = "")
title(main=list("Séquences de la Différence entre la Difficulté Prédite par l'Enseignant et la Difficulté Réelle",  cex = 2.5, font = 3))
axis(1, at = 0.5:8.5, labels = paste(unique(prep_Sequences_mod3chap2$Quizz_ID), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40), labels = paste(seq_Sequences_mod3chap2_PR$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang et Identification du Quiz dans la Séquence Pédagogique", cex.lab = 2.5, line = 5)
title(ylab = "Année", cex.lab = 2.5, line = 7)

#Plot the Seqlegend Predicted/Real Difficulty and Define its title
seqlegend(mvad.Sequences_mod3chap2_PR, cpal = legend_color_PR, ltext = legend_order_PR, cex = 2.5, position = 'center')
text(1, 0.35, paste("Différence Prédiction/Réalité"), cex = 2.5)

#Put the main Title of the Figure
mtext(title_Sequences_mod3chap2_PR, outer=TRUE,  cex=1.8, font = 1, line=3)

#Save the Figure
dev.off()
```

################################################################
#Build the Figure of the Predicted/Real and Adapted Difficulty #
################################################################
```{r}
#Figure of the Predicted/Real and Adapted Difficulty

#Define the name of the file
fig_Sequences_mod3chap2_PR_A = paste("Seq-PR_A-Chap_", unique(prep_Sequences_mod3chap2$Chapter_ID),
                                   "-Mod_", unique(prep_Sequences_mod3chap2$Module_ID),
                                   "-Dep_", unique(prep_Sequences_mod3chap2$Departement), "-2015_2020", sep = "")

#Set the Figure file name and Figure size, margins and positions of the graphs
png(paste("../Figures/", fig_Sequences_mod3chap2_PR_A, ".png", sep = ""), heigh = 800, width = 1300)
layout(matrix(c(1, 1, 1, 1, 1, 1, 1, 2, 2, 2, 3, 3, 3, 3, 3, 3, 3, 4, 4, 4), ncol=10, byrow=TRUE))
par(mar=c(9,9,3,0)+0.1, oma=c(0,1,9,0))

#Define the title of the Figure
title_Sequences_mod3chap2_PR_A = paste(
  "Séquences respectives de la Différence entre la Difficulté Prédite par rapport à la Difficulté Réelle et la Validation de 2015 à 2020, \n",
  "de chaque Quiz du chapitre", paste("«", unique(prep_Sequences_mod3chap2$Chapter), "»,", sep = ""), 
  "du module", paste("«", unique(prep_Sequences_mod3chap2$Module), "»,", sep = ""),
  "du Département", paste("d'", unique(prep_Sequences_mod3chap2$Departement), ".", sep = ""))

#Plot the Seqplot Predicted/Real Difficulty and Define its axis and labels
seqplot(mvad.Sequences_mod3chap2_PR, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_mod3chap2_PR)),
        cpal = seqplot_color_PR, space = 0.15, main = "")
title(main=list("Séquences de la Différence entre la Difficulté Prédite par l'Enseignant et la Difficulté Réelle",  cex = 2.5, font = 3))
axis(1, at = 0.5:8.5, labels = paste(unique(prep_Sequences_mod3chap2$Quizz_ID), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40), labels = paste(seq_Sequences_mod3chap2_PR$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang et Identification du Quiz dans la Séquence Pédagogique", cex.lab = 2.5, line = 5)
title(ylab = "Année", cex.lab = 2.5, line = 7)

#Plot the Seqlegend Predicted/Real Difficulty and Define its title
seqlegend(mvad.Sequences_mod3chap2_PR, cpal = legend_color_PR, ltext = legend_order_PR, cex = 2.5, position = 'center')
text(1, 0.80, paste("Différence Prédiction/Réalité"), cex = 2.5)

#Plot the Seqplot Adapted Difficulty and Define its axis and labels
seqplot(mvad.Sequences_mod3chap2_Adapted, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_mod3chap2_Adapted)),
        cpal = seqplot_color_Adapted, space = 0.15)
title(main=list("Séquences de Validation de la Difficulté",  cex = 2.5, font = 3))
axis(1, at = 0.5:8.5, labels = paste(unique(prep_Sequences_mod3chap2$Quizz_ID), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40), labels = paste(seq_Sequences_mod3chap2_Adapted$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang et Identification du Quiz dans la Séquence Pédagogique", cex.lab = 2.5, line = 5)
title(ylab = "Année", cex.lab = 2.5, line = 7)

#Plot the Seqlegend Adapted Difficulty and Define its title
seqlegend(mvad.Sequences_mod3chap2_Adapted, cpal = legend_color_Adapted, ltext = legend_order_Adapted, cex = 2.5, position = 'center')
text(1, 0.5, paste("Validation de la Difficulté"), cex = 2.5)

#Put the main Title of the Figure
mtext(title_Sequences_mod3chap2_PR_A, outer=TRUE,  cex=1.8, font = 1, line=3)

#Save the Figure
dev.off()
```

#############################################################
#Build the Figure of the Predicted/Real and Type of Quizzes #
#############################################################
```{r}
# Figure of the Predicted/Real and Type of Quizzes

#Define the name of the file
fig_Sequences_mod3chap2_PR_T = paste("Seq-PR_T-Chap_", unique(prep_Sequences_mod3chap2$Chapter_ID),
                                   "-Mod_", unique(prep_Sequences_mod3chap2$Module_ID),
                                   "-Dep_", unique(prep_Sequences_mod3chap2$Departement), "-2015_2020", sep = "")

#Set the Figure file name and Figure size, margins and positions of the graphs
png(paste("../Figures/", fig_Sequences_mod3chap2_PR_T, ".png", sep = ""), heigh = 800, width = 1300)
layout(matrix(c(1, 1, 1, 1, 1, 1, 1, 2, 2, 2, 3, 3, 3, 3, 3, 3, 3, 4, 4, 4), ncol=10, byrow=TRUE))
par(mar=c(9,9,3,0)+0.1, oma=c(0,1,9,0))

#Define the title of the Figure
title_Sequences_mod3chap2_PR_T = paste(
  "Séquences respectives de la Différence entre la Difficulté Prédite par rapport à la Difficulté Réelle et le Type de 2015 à 2020, \n",
  "de chaque Quiz du chapitre", paste("«", unique(prep_Sequences_mod3chap2$Chapter), "»,", sep = ""), 
  "du module", paste("«", unique(prep_Sequences_mod3chap2$Module), "»,", sep = ""),
  "du Département", paste("d'", unique(prep_Sequences_mod3chap2$Departement), ".", sep = ""))


#Plot the Seqplot Predicted/Real Difficulty and Define its axis and labels
seqplot(mvad.Sequences_mod3chap2_PR, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_mod3chap2_PR)),
        cpal = seqplot_color_PR, space = 0.15, main = "")
title(main=list("Séquences de la Différence entre la Difficulté Prédite par l'Enseignant et la Difficulté Réelle",  cex = 2.5, font = 3))
axis(1, at = 0.5:8.5, labels = paste(unique(prep_Sequences_mod3chap2$Quizz_ID), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40), labels = paste(seq_Sequences_mod3chap2_PR$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang et Identification du Quiz dans la Séquence Pédagogique", cex.lab = 2.5, line = 5)
title(ylab = "Année", cex.lab = 2.5, line = 7)

#Plot the Seqlegend Predicted/Real Difficulty and Define its title
seqlegend(mvad.Sequences_mod3chap2_PR, cpal = legend_color_PR, ltext = legend_order_PR, cex = 2.5, position = 'center')
text(1, 0.80, paste("Différence Prédiction/Réalité"), cex = 2.5)

#Plot the Seqplot Type of Quizzes and Define its axis and labels
seqplot(mvad.Sequences_mod3chap2_Type, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_mod3chap2_Type)),
        cpal = seqplot_color_Type, space = 0.15)
title(main=list("Séquences du Type de Quiz",  cex = 2.5, font = 3))
axis(1, at = 0.5:8.5, labels = paste(unique(prep_Sequences_mod3chap2$Quizz_ID), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40), labels = paste(seq_Sequences_mod3chap2_Type$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang et Identification du Quiz dans la Séquence Pédagogique", cex.lab = 2.5, line = 5)
title(ylab = "Année", cex.lab = 2.5, line = 7)

#Plot the Seqlegend Type of Quizzes and Define its title
seqlegend(mvad.Sequences_mod3chap2_Type, cpal = legend_color_Type, ltext = legend_order_Type, cex = 2.5, position = 'center')
text(1, 0.7, paste("Type du Quiz"), cex = 2.55)

#Put the main Title of the Figure
mtext(title_Sequences_mod3chap2_PR_T, outer=TRUE,  cex=1.8, font = 1, line=3)

#Save the Figure
dev.off()
```

########################################################################
#Build the Figure of the Predicted, Real Difficulty and Predicted/Real #
########################################################################
```{r}
#Figure of the Predicted, Real Difficulty and Predicted/Real

#Define the name of the file
fig_Sequences_mod3chap2_P_R_PR = paste("Seq-P_R_PR-Chap_", unique(prep_Sequences_mod3chap2$Chapter_ID),
                                   "-Mod_", unique(prep_Sequences_mod3chap2$Module_ID),
                                   "-Dep_", unique(prep_Sequences_mod3chap2$Departement), "-2015_2020", sep = "")

#Set the Figure file name and Figure size, margins and positions of the graphs
png(paste("../Figures/", fig_Sequences_mod3chap2_P_R_PR, ".png", sep = ""), heigh = 800, width = 1800)
layout(matrix(c(1, 1, 1, 1, 1, 1, 6, 2, 2, 2, 2, 2, 2, 3, 3, 3, 6, 4, 4, 4, 4, 4, 4, 4, 4, 4, 5, 5, 5, 5, 5, 6), ncol=16, byrow=TRUE))
par(mar=c(9,9,3,0)+0.1, oma=c(0,1,9,0))

#Define the title of the Figure
title_Sequences_mod3chap2_P_R_PR = paste(
  "Séquences respectives de la Prédiction, de la Réalité et de la Différence de Difficulté Associée de 2015 à 2020, \n",
  "de chaque Quiz du chapitre", paste("«", unique(prep_Sequences_mod3chap2$Chapter), "»,", sep = ""), 
  "du module", paste("«", unique(prep_Sequences_mod3chap2$Module), "»,", sep = ""),
  "du Département", paste("d'", unique(prep_Sequences_mod3chap2$Departement), ".", sep = ""))

#Plot the Seqplot Predicted Difficulty and Define its axis and labels
seqplot(mvad.Sequences_mod3chap2_Predicted, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_mod3chap2_Predicted)),
        cpal = seqplot_color_Predicted, space = 0.15)
title(main=list("Séquences de la Difficulté Prédite par l'Enseignant",  cex = 2.5, font = 3))
axis(1, at = 0.5:8.5, labels = paste(unique(prep_Sequences_mod3chap2$Quizz_ID), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40), labels = paste(seq_Sequences_mod3chap2_Predicted$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang et Identification du Quiz dans la Séquence Pédagogique", cex.lab = 2.5, line = 5)
title(ylab = "Année", cex.lab = 2.5, line = 7)

#Plot the Seqplot Real Difficulty and Define its axis and labels
seqplot(mvad.Sequences_mod3chap2_Real, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_mod3chap2_Real)),
        cpal = seqplot_color_Real, space = 0.15)
title(main=list("Séquences de la Difficulté Réelle",  cex = 2.5, font = 3))
axis(1, at = 0.5:8.5, labels = paste(unique(prep_Sequences_mod3chap2$Quizz_ID), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40), labels = paste(seq_Sequences_mod3chap2_Real$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang et Identification du Quiz dans la Séquence Pédagogique", cex.lab = 2.5, line = 5)
title(ylab = "Année", cex.lab = 2.5, line = 7)

#Plot the Seqlegend Predicted or Real Difficulty and Define its title
seqlegend(mvad.Sequences_mod3chap2_Predicted, cpal = legend_color_Predicted, ltext = legend_order_Predicted, cex = 2.5, position = 'center')
text(1, 0.60, paste("Niveau de Difficulté"), cex = 2.5)

#Plot the Seqplot Predicted/Real Difficulty and Define its axis and labels
seqplot(mvad.Sequences_mod3chap2_PR, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_mod3chap2_PR)),
        cpal = seqplot_color_PR, space = 0.15, main = "")
title(main=list("Séquences de la Différence entre la Difficulté Prédite par l'Enseignant et la Difficulté Réelle",  cex = 2.5, font = 3))
axis(1, at = 0.5:8.5, labels = paste(unique(prep_Sequences_mod3chap2$Quizz_ID), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40), labels = paste(seq_Sequences_mod3chap2_PR$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang et Identification du Quiz dans la Séquence Pédagogique", cex.lab = 2.5, line = 5)
title(ylab = "Année", cex.lab = 2.5, line = 7)

#Plot the Seqlegend Predicted/Real Difficulty and Define its title
seqlegend(mvad.Sequences_mod3chap2_PR, cpal = legend_color_PR, ltext = legend_order_PR, cex = 2.5, position = 'center')
text(1, 0.80, paste("Différence Prédiction/Réalité"), cex = 2.5)

#Plot an empty graph 
plot.new()

#Put the main Title of the Figure
mtext(title_Sequences_mod3chap2_P_R_PR, outer=TRUE,  cex=2.2, font = 1, line=2)

#Save the Figure
dev.off()
```

###################################################################
#Build the Figure of the Predicted Difficulty and Real Difficulty #
###################################################################
```{r}
#Figure of the Predicted Difficulty and Real Difficulty

#Define the name of the file
fig_Sequences_mod3chap2_P_R = paste("Seq-P_R-Chap_", unique(prep_Sequences_mod3chap2$Chapter_ID),
                                   "-Mod_", unique(prep_Sequences_mod3chap2$Module_ID),
                                   "-Dep_", unique(prep_Sequences_mod3chap2$Departement), "-2015_2020", sep = "")

#Set the Figure file name and Figure size, margins and positions of the graphs
png(paste("../Figures/", fig_Sequences_mod3chap2_P_R, ".png", sep = ""), heigh = 600, width = 1600)
layout(matrix(c(1, 1, 1, 1, 1, 1, 4, 2, 2, 2, 2, 2, 2, 3, 3, 3), ncol=16, byrow=TRUE))
par(mar=c(9,9,3,0)+0.1, oma=c(0,1,9,0))

#Define the title of the Figure
title_Sequences_mod3chap2_P_R = paste(
  "Séquences respectives du Niveau de Difficulté Prédit et du Niveau de Difficulté Réel de 2015 à 2020, \n",
  "de chaque Quiz du chapitre", paste("«", unique(prep_Sequences_mod3chap2$Chapter), "»,", sep = ""), 
  "du module", paste("«", unique(prep_Sequences_mod3chap2$Module), "»,", sep = ""),
  "du Département", paste("d'", unique(prep_Sequences_mod3chap2$Departement), ".", sep = ""))

#Plot the Seqplot Predicted Difficulty and Define its axis and labels
seqplot(mvad.Sequences_mod3chap2_Predicted, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_mod3chap2_Predicted)),
        cpal = seqplot_color_Predicted, space = 0.15)
title(main=list("Séquences de la Difficulté Prédite par l'Enseignant",  cex = 2.5, font = 3))
axis(1, at = 0.5:8.5, labels = paste(unique(prep_Sequences_mod3chap2$Quizz_ID), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40), labels = paste(seq_Sequences_mod3chap2_Predicted$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang et Identification du Quiz dans la Séquence Pédagogique", cex.lab = 2.5, line = 5)
title(ylab = "Année", cex.lab = 2.5, line = 7)

#Plot the Seqplot Real Difficulty and Define its axis and labels
seqplot(mvad.Sequences_mod3chap2_Real, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_mod3chap2_Real)),
        cpal = seqplot_color_Real, space = 0.15)
title(main=list("Séquences de la Difficulté Réelle",  cex = 2.5, font = 3))
axis(1, at = 0.5:8.5, labels = paste(unique(prep_Sequences_mod3chap2$Quizz_ID), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40), labels = paste(seq_Sequences_mod3chap2_Real$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang et Identification du Quiz dans la Séquence Pédagogique", cex.lab = 2.5, line = 5)
title(ylab = "Année", cex.lab = 2.5, line = 7)

#Plot the Seqlegend Predicted or Real Difficulty and Define its title
seqlegend(mvad.Sequences_mod3chap2_Predicted, cpal = legend_color_Predicted, ltext = legend_order_Predicted, cex = 2.5, position = 'center')
text(1, 0.60, paste("Niveau de Difficulté"), cex = 2.5)

#Plot an empty graph 
plot.new()

#Put the main Title of the Figure
mtext(title_Sequences_mod3chap2_P_R, outer=TRUE,  cex=2.2, font = 1, line=2)

#Save the Figure
dev.off()
```