---
title: "Teaching Analytics"
author: "ROUX Dorian"
output: html_document
---

**Libraries**
```{r}
#Import the Libraries.
library('readr')
library('dplyr')
library("tidyr")
library("RColorBrewer")
library('TraMineR')
library('ggplot2')
```


**CSV**
```{r}
#Import the DataFrame.
prep_Sequences <- select(read_csv('../Data/Prepared_Sequences.csv'), -c(1)) #Import the required CSV and Remove the first column that represents the index.

head(prep_Sequences, 10) #Display the ten first rows.
```

**Spread and Write**
```{r}
#Save a a Spread Dataframe.
seq_Spread <- spread(prep_Sequences, Resources_Rank,Resources_Type_Basic) #Spread the previous Dataframe.
write.csv(seq_Spread,'../Data/Spead_Sequences.csv', row.names = FALSE) #Save the Spread Dataframe into a CSV file
```


**Prepare the Variables**
```{r}
#Rename the Sequence Type
Seq <- prep_Sequences

Seq$Resources_Type_Basic[Seq$Resources_Type_Basic == 'Lecture'] <- 'en Presentiel: Leçon' 
Seq$Resources_Type_Basic[Seq$Resources_Type_Basic == 'Exercise'] <- 'en Presentiel: Exercices' 
Seq$Resources_Type_Basic[Seq$Resources_Type_Basic == 'Examen'] <- 'en Presentiel: Examen'  

Seq$Resources_Type_Basic[Seq$Resources_Type_Basic == 'Video'] <- 'en Ligne: Video'
Seq$Resources_Type_Basic[Seq$Resources_Type_Basic == 'QCM'] <- "en Ligne: Banque d'Exercices" 
Seq$Resources_Type_Basic[Seq$Resources_Type_Basic == 'Test'] <- 'en Ligne: Test'
```

```{r}
#Set the Legend Color and Order in both French and English.

legend_color = c('#FFB396', '#FF7878', '#FF0000', '#000FFF', '#7878FF', '#96B3FF') #Color of the legend.

legend_order_FR = c('en Présentiel: Leçon', 'en Présentiel: Exercices', 'en Présentiel: Examen', 'en Ligne: Test', "en Ligne: Banque d'Exercices", 'en Ligne: Vidéo') #Order of the legend in French.

legend_order_EN = c('in Class: Lecture', 'in Class: Exercises', 'in Class: Exam', 'in Distance: Test', 'in Distance: Quizzes', 'in Distance: Video') #Order of the legend in English
```



*Define the Sequences*

**Learning Sequences of the Module 11 teached by Mme GALLE from the Department of Computer Science**
```{r}
#Sequences 11
prep_Sequences_11 <- Seq %>% filter(Course_ID == 11) #Filter the dataset.
seq_Sequences_11 <- spread(prep_Sequences_11, Resources_Rank,Resources_Type_Basic) #Spread the values from one column into columns.
mvad.Sequences_11 <- seqdef(seq_Sequences_11[, -c(1:6)]) # Transform the new columns into sequences.

#Set the Seqplot Color
seqplot_color_11 = c('#7878FF', '#000FFF', '#96B3FF', '#FF7878', '#FFB396') #Color of the figure.
```

**Learning Sequences of the Module 35 teached by Mme FAVRET from the Department of Computer Science**
```{r}
#Sequences 35
prep_Sequences_35 <- Seq %>% filter(Course_ID == 35) #Filter the dataset.
seq_Sequences_35 <- spread(prep_Sequences_35, Resources_Rank,Resources_Type_Basic) #Spread the values from one column into columns.
mvad.Sequences_35 <- seqdef(seq_Sequences_35[, -c(1:6)]) # Transform the new columns into sequences.

#Set the Seqplot Color
seqplot_color_35 = c('#96B3FF', '#FF0000', '#FF7878', '#FFB396') #Color of the figure.
```

**Learning Sequences of the Module 38 teached by Mme FAVRET from the Department of Computer Science**
```{r}
#Sequences 38
prep_Sequences_38 <- Seq %>% filter(Course_ID == 38) #Filter the dataset.
seq_Sequences_38 <- spread(prep_Sequences_38, Resources_Rank,Resources_Type_Basic) #Spread the values from one column into columns.
mvad.Sequences_38 <- seqdef(seq_Sequences_38[, -c(1:6)]) # Transform the new columns into sequences.

#Set the Seqplot Color
seqplot_color_38 = c('#7878FF', '#96B3FF', '#FF7878', '#FFB396') #Color of the figure.
```

**Learning Sequences of the Module 41 teached by Mme FAVRET from the Department of Computer Science**
```{r}
#Sequences 41
prep_Sequences_41 <- Seq %>% filter(Course_ID == 41) #Filter the dataset.
seq_Sequences_41 <- spread(prep_Sequences_41, Resources_Rank,Resources_Type_Basic) #Spread the values from one column into columns.
mvad.Sequences_41 <- seqdef(seq_Sequences_41[, -c(1:6)]) # Transform the new columns into sequences.

#Set the Seqplot Color
seqplot_color_41 = c('#7878FF', '#000FFF', '#96B3FF', '#FF0000', '#FF7878', '#FFB396') #Color of the figure.
```

**Learning Sequences of the Module 60 teached by Mr ROGIER from the Department of Computer Science**
```{r}
#Sequences 60
prep_Sequences_60 <- Seq %>% filter(Course_ID == 60) #Filter the dataset.
seq_Sequences_60 <- spread(prep_Sequences_60, Resources_Rank,Resources_Type_Basic) #Spread the values from one column into columns.
mvad.Sequences_60 <- seqdef(seq_Sequences_60[, -c(1:6)]) # Transform the new columns into sequences.

#Set the Seqplot Color
seqplot_color_60 = c('#7878FF', '#96B3FF', '#FF0000', '#FF7878', '#FFB396') #Color of the figure.
```

**Learning Sequences of the Module 61 teached by Mr ROGIER from the Department of Computer Science**
```{r}
#Sequences 61
prep_Sequences_61 <- Seq %>% filter(Course_ID == 61) #Filter the dataset.
seq_Sequences_61 <- spread(prep_Sequences_61, Resources_Rank,Resources_Type_Basic) #Spread the values from one column into columns.
mvad.Sequences_61 <- seqdef(seq_Sequences_61[, -c(1:6)]) # Transform the new columns into sequences.

#Set the Seqplot Color
seqplot_color_61 = c('#7878FF', '#000FFF', '#96B3FF', '#FF7878', '#FFB396') #Color of the figure.
```

**Learning Sequences of the Module 69 teached by Mr ROGIER from the Department of Computer Science**
```{r}
#Sequences 69
prep_Sequences_69 <- Seq %>% filter(Course_ID == 69) #Filter the dataset.
seq_Sequences_69 <- spread(prep_Sequences_69, Resources_Rank,Resources_Type_Basic) #Spread the values from one column into columns.
mvad.Sequences_69 <- seqdef(seq_Sequences_69[, -c(1:6)]) # Transform the new columns into sequences.

#Set the Seqplot Color
seqplot_color_69 = c('#7878FF', '#96B3FF', '#FF0000', '#FF7878', '#FFB396') #Color of the figure.
```

**Learning Sequences of the Module 80 teached by Mr AMIRAULT from the Department of Computer Science**
```{r}
#Sequences 80
prep_Sequences_80 <- Seq %>% filter(Course_ID == 80) #Filter the dataset.
seq_Sequences_80 <- spread(prep_Sequences_80, Resources_Rank,Resources_Type_Basic) #Spread the values from one column into columns.
mvad.Sequences_80 <- seqdef(seq_Sequences_80[, -c(1:6)]) # Transform the new columns into sequences.

#Set the Seqplot Color
seqplot_color_80 = c('#96B3FF', '#FF7878', '#FFB396') #Color of the figure.
```

**Learning Sequences of the Module 386 teached by Mr Verdin from the Department of History**
```{r}
#Sequences 386
prep_Sequences_386 <- Seq %>% filter(Course_ID == 386) #Filter the dataset.
seq_Sequences_386 <- spread(prep_Sequences_386, Resources_Rank,Resources_Type_Basic) #Spread the values from one column into columns.
mvad.Sequences_386 <- seqdef(seq_Sequences_386[, -c(1:6)]) # Transform the new columns into sequences.

#Set the Seqplot Color
seqplot_color_386 = c('#7878FF', '#000FFF', '#96B3FF', '#FF0000', '#FF7878', '#FFB396') #Color of the figure.
```



**Build the Figure**

**Learning Sequences of the Module 386 teached by Mr VERDIN from the Department of History**

#################
#French Version #
#################
```{r}
#Figure of the Learning Sequences of the Module 386 teached by Mr VERDIN from the Department of History

#Define the name of the file
fig_Sequences_386 = paste("Sequences-Module_386-Teacher_VERDIN-Dept_History", sep = "")

#Set the Figure file name and Figure size, margins and positions of the graphs
png(paste("../Figures/Vrs_Français/", fig_Sequences_386, ".png", sep = ""), heigh = 700, width = 1400)
layout(matrix(c(1, 1, 1, 1, 2, 2), ncol=6, byrow=TRUE))
par(mar=c(8,9,0,0)+0.1, oma=c(0,1,6,0))

#Define the title of the Figure
title_fig_Sequences_386 =  "Séquences Pédagogiques de 2013 à 2020 pour le Module «386» enseigné par Mr VERDIN du Département d'Histoire"

#Plot the Seqplot and Define its axis and labels
seqplot(mvad.Sequences_386, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_386)),
        cpal = seqplot_color_386, space = 0.15, main = "")
axis(1, at = 0.5:(max(prep_Sequences_386$Resources_Rank) - 0.5), labels = paste(unique(prep_Sequences_386$Resources_Rank), sep = ""), cex.axis = 2.3, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_386$Year, sep = ""), las = 1,  cex.axis = 2.3, line = 0, tick = FALSE)
title(xlab = "Rang des Ressources dans la Séquence Pédagogique", cex.lab = 2.5, line = 5)
title(ylab = "Années", cex.lab = 2.5, line = 7)

#Plot the Seqlegend Difficulty and Define its title
seqlegend(seqdef(legend_order_FR), cpal = legend_color, ltext = legend_order_FR, cex = 2.5, position = 'center')
text(1, 0.40, paste("Type des Ressources"), cex = 2.5)

#Put the main Title of the Figure
mtext(title_fig_Sequences_386, outer=TRUE,  cex=2, font = 1, line=0)

#Save the Figure
dev.off()
```

##################
#English Version #
##################
```{r}
#Figure of the Learning Sequences of the Module 386 teached by Mr VERDIN from the Department of History

#Define the name of the file
fig_Sequences_386 = paste("Sequences-Module_386-Teacher_VERDIN-Dept_History", sep = "")

#Set the Figure file name and Figure size, margins and positions of the graphs
png(paste("../Figures/Vrs_English/", fig_Sequences_386, ".png", sep = ""), heigh = 700, width = 1400)
layout(matrix(c(1, 1, 1, 1, 2, 2), ncol=6, byrow=TRUE))
par(mar=c(8,9,0,0)+0.1, oma=c(0,1,6,0))

#Define the title of the Figure
title_fig_Sequences_386 = "Learning Sequences from 2013 to 2020 for the Module «386» teached by Mr VERDIN of the Department of History"

#Plot the Seqplot and Define its axis and labels
seqplot(mvad.Sequences_386, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_386)),
        cpal = seqplot_color_386, space = 0.15, main = "")
axis(1, at = 0.5:(max(prep_Sequences_386$Resources_Rank) - 0.5), labels = paste(unique(prep_Sequences_386$Resources_Rank), sep = ""), cex.axis = 2.3, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_386$Year, sep = ""), las = 1,  cex.axis = 2.3, line = 0, tick = FALSE)
title(xlab = "Rank of the Ressources in the Learning Sequence", cex.lab = 2.5, line = 5)
title(ylab = "Years", cex.lab = 2.5, line = 7)

#Plot the Seqlegend and Define its title
seqlegend(seqdef(legend_order_EN), cpal = legend_color, ltext = legend_order_EN, cex = 2.5, position = 'center')
text(1, 0.40, paste("Type of Ressources"), cex = 2.5)

#Put the main Title of the Figure
mtext(title_fig_Sequences_386, outer=TRUE,  cex=2, font = 1, line=0)

#Save the Figure
dev.off()
```


**Learning Sequences of the Module 41 teached by Mme FAVRET from the Department of Computer Science**

#################
#French Version #
#################
```{r}
#Figure of the Learning Sequences of the Module 41 teached by Mme FAVRET from the Department of Computer Science

#Define the name of the file
fig_Sequences_41 = paste("Sequences-Module_41-Teacher_FAVRET-Dept_ComputerScience", sep = "")

#Set the Figure file name and Figure size, margins and positions of the graphs
png(paste("../Figures/Vrs_Français/", fig_Sequences_41, ".png", sep = ""), heigh = 700, width = 1400)
layout(matrix(c(1, 1, 1, 1, 2, 2), ncol=6, byrow=TRUE))
par(mar=c(8,9,0,0)+0.1, oma=c(0,1,7,0))
par(family="serif")
#Define the title of the Figure
title_fig_Sequences_41 =  "Séquences Pédagogiques de 2013 à 2020 du Cours n°41 intitulé «Introduction à la Programmation» \n enseigné par Mme FAVRET du Département d'Informatique"

#Plot the Seqplot and Define its axis and labels
seqplot(mvad.Sequences_41, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_41)),
        cpal = seqplot_color_41, space = 0.15, main = "")
axis(1, at = 0.5:(max(prep_Sequences_41$Resources_Rank) - 0.5), labels = paste(unique(prep_Sequences_41$Resources_Rank), sep = ""), cex.axis = 2.8, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_41$Year, sep = ""), las = 1,  cex.axis = 2.8, line = 0, tick = FALSE)
title(xlab = "Rang des Ressources dans la Séquence Pédagogique", cex.lab = 3, line = 5)
title(ylab = "Années", cex.lab = 3, line = 7)

#Plot the Seqlegend and Define its title
seqlegend(seqdef(legend_order_FR), cpal = legend_color, ltext = legend_order_FR, cex = 2.8, position = 'center')
text(1, 0.45, paste("Type des Ressources"), cex = 3)

#Put the main Title of the Figure
mtext(title_fig_Sequences_41, outer=TRUE,  cex=2.3, font = 1, line=0)

#Save the Figure
dev.off()
```

##################
#English Version #
##################
```{r}
#Figure of the Learning Sequences of the Module 41 teached by Mme FAVRET from the Department of Computer Science

#Define the name of the file
fig_Sequences_41 = paste("Sequences-Module_41-Teacher_FAVRET-Dept_ComputerScience", sep = "")

#Set the Figure file name and Figure size, margins and positions of the graphs
png(paste("../Figures/Vrs_English/", fig_Sequences_41, ".png", sep = ""), heigh = 700, width = 1400)
layout(matrix(c(1, 1, 1, 1, 2, 2), ncol=6, byrow=TRUE))
par(mar=c(8,9,0,0)+0.1, oma=c(0,1,6,0))

#Define the title of the Figure
title_fig_Sequences_41 = "Learning Sequences from 2013 to 2020 for the Module «41» teached by Mme FAVRET of the Department of Computer Science"

#Plot the Seqplot and Define its axis and labels
seqplot(mvad.Sequences_41, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_41)),
        cpal = seqplot_color_41, space = 0.15, main = "")
axis(1, at = 0.5:(max(prep_Sequences_41$Resources_Rank) - 0.5), labels = paste(unique(prep_Sequences_41$Resources_Rank), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_41$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rank of the Ressources in the Learning Sequence", cex.lab = 2.5, line = 5)
title(ylab = "Years", cex.lab = 2.5, line = 7)

#Plot the Seqlegend and Define its title
seqlegend(seqdef(legend_order_EN), cpal = legend_color, ltext = legend_order_EN, cex = 2.5, position = 'center')
text(1, 0.40, paste("Type of Ressources"), cex = 2.5)

#Put the main Title of the Figure
mtext(title_fig_Sequences_41, outer=TRUE,  cex=2, font = 1, line=0)

#Save the Figure
dev.off()
```


**Learning Sequences of the Modules 60, 61 and 69 teached by Mr ROGIER from the Department of Computer Science**

#################
#French Version #
#################
```{r}
#Figure of the Learning Sequences of the Modules 60, 61 and 69 teached by Mr ROGIER from the Department of Computer Science

#Define the name of the file
fig_Sequences_60_61_69 = paste("Sequences-Modules_60_61_69-Teacher_Rogier-Dept_ComputerScience", sep = "")

#Set the Figure file name and Figure size, margins and positions of the graphs
png(paste("../Figures/Vrs_Français/", fig_Sequences_60_61_69, ".png", sep = ""), heigh = 700, width = 1400)
layout(matrix(c(1, 1, 2, 2, 3, 3, 4, 4), ncol=4, byrow=TRUE))
par(mar=c(8,9,3,5)+0.1, oma=c(0,1,8,1))

#Define the title of the Figure
title_fig_Sequences_60_61_69 = paste("Séquences Pédagogiques de 2013 à 2020, \n pour les Modules «60», «61» et «69» enseignés par Mr ROGIER du Département d'Informatique", sep = "")

#Plot the Seqplot of the Module 60 and Define its axis and labels
seqplot(mvad.Sequences_60, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_60)),
        cpal = seqplot_color_60, space = 0.15, main = "")
title(main=list("Séquences Pédagogiques pour le Module «60»",  cex = 2.5, font = 3))
axis(1, at = 0.5:(max(prep_Sequences_60$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_60$Resources_Rank), sep = ""), cex.axis = 2.3, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_60$Year, sep = ""), las = 1,  cex.axis = 2.3, line = 0, tick = FALSE)
title(xlab = "Rang des Ressources dans les Séquences Pédagogiques", cex.lab = 2.5, line = 5)
title(ylab = "Années", cex.lab = 2.5, line = 7)

#Plot the Seqplot of the Module 61 and Define its axis and labels
seqplot(mvad.Sequences_61, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_61)),
        cpal = seqplot_color_61, space = 0.15, main = "")
title(main=list("Séquences Pédagogiques pour le Module «61»",  cex = 2.5, font = 3))
axis(1, at = 0.5:(max(prep_Sequences_61$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_61$Resources_Rank), sep = ""), cex.axis = 2.3, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_61$Year, sep = ""), las = 1,  cex.axis = 2.3, line = 0, tick = FALSE)
title(xlab = "Rang des Ressources dans les Séquences Pédagogiques", cex.lab = 2.5, line = 5)
title(ylab = "Années", cex.lab = 2.5, line = 7)

#Plot the Seqplot of the Module 69 and Define its axis and labels
seqplot(mvad.Sequences_69, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_69)),
        cpal = seqplot_color_69, space = 0.15, main = "")
title(main=list("Séquences Pédagogiques pour le Module «69»",  cex = 2.5, font = 3))
axis(1, at = 0.5:(max(prep_Sequences_69$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_69$Resources_Rank), sep = ""), cex.axis = 2.3, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_69$Year, sep = ""), las = 1,  cex.axis = 2.3, line = 0, tick = FALSE)
title(xlab = "Rang des Ressources dans les Séquences Pédagogiques", cex.lab = 2.5, line = 5)
title(ylab = "Années", cex.lab = 2.5, line = 7)

#Plot the Seqlegend of the Sequences and Define its title
seqlegend(seqdef(legend_order_FR), cpal = legend_color, ltext = legend_order_FR, cex = 2.5, position = 'center')
text(1, 1, paste("Type des Ressources"), cex = 2.5)

#Put the main Title of the Figure
mtext(title_fig_Sequences_60_61_69, outer=TRUE,  cex=2, font = 1, line=2)

#Save the Figure
dev.off()
```

##################
#English Version #
##################
```{r}
#Figure of the Learning Sequences of the Modules 60, 61 and 69 teached by Mr ROGIER from the Department of Computer Science

#Define the name of the file
fig_Sequences_60_61_69 = paste("Sequences-Modules_60_61_69-Teacher_Rogier-Dept_ComputerScience", sep = "")

#Set the Figure file name and Figure size, margins and positions of the graphs
png(paste("../Figures/Vrs_English/", fig_Sequences_60_61_69, ".png", sep = ""), heigh = 700, width = 1400)
layout(matrix(c(1, 1, 2, 2, 3, 3, 4, 4), ncol=4, byrow=TRUE))
par(mar=c(8,9,3,5)+0.1, oma=c(0,1,8,1))

#Define the title of the Figure
title_fig_Sequences_60_61_69 = paste("Learning Sequences from 2013 to 2020, \n for the Modules «60», «61» et «69» teached by Mr ROGIER from the Department of Computer Science", sep = "")

#Plot the Seqplot of the Module 60 and Define its axis and labels
seqplot(mvad.Sequences_60, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_60)),
        cpal = seqplot_color_60, space = 0.15, main = "")
title(main=list("Learning Sequences for the Module «60» from 2013 to 2020",  cex = 2.5, font = 3))
axis(1, at = 0.5:(max(prep_Sequences_60$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_60$Resources_Rank), sep = ""), cex.axis = 2.3, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_60$Year, sep = ""), las = 1,  cex.axis = 2.3, line = 0, tick = FALSE)
title(xlab = "Rank of the Ressources in the Learning Sequences", cex.lab = 2.5, line = 5)
title(ylab = "Years", cex.lab = 2.5, line = 7)

#Plot the Seqplot of the Module 61 and Define its axis and labels
seqplot(mvad.Sequences_61, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_61)),
        cpal = seqplot_color_61, space = 0.15, main = "")
title(main=list("Learning Sequences for the Module «61» from 2013 to 2020",  cex = 2.5, font = 3))

axis(1, at = 0.5:(max(prep_Sequences_61$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_61$Resources_Rank), sep = ""), cex.axis = 2.3, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_61$Year, sep = ""), las = 1,  cex.axis = 2.3, line = 0, tick = FALSE)
title(xlab = "Rank of the Resources in the Learning Sequences", cex.lab = 2.5, line = 5)
title(ylab = "Years", cex.lab = 2.5, line = 7)

#Plot the Seqplot of the Module 69 and Define its axis and labels
seqplot(mvad.Sequences_69, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_69)),
        cpal = seqplot_color_69, space = 0.15, main = "")
title(main=list("Learning Sequences for the Module «69» from 2013 to 2020",  cex = 2.5, font = 3))
axis(1, at = 0.5:(max(prep_Sequences_69$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_69$Resources_Rank), sep = ""), cex.axis = 2.3, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_69$Year, sep = ""), las = 1,  cex.axis = 2.3, line = 0, tick = FALSE)
title(xlab = "Rank of the Resources in the Learning Sequences", cex.lab = 2.5, line = 5)
title(ylab = "Years", cex.lab = 2.5, line = 7)

#Plot the Seqlegend of the Sequences and Define its title
seqlegend(seqdef(legend_order_EN), cpal = legend_color, ltext = legend_order_EN, cex = 2.5, position = 'center')
text(1, 1, paste("Type of Resources"), cex = 2.5)

#Put the main Title of the Figure
mtext(title_fig_Sequences_60_61_69, outer=TRUE,  cex=2, font = 1, line=2)

#Save the Figure
dev.off()
```


**Learning Sequences of the Modules 35, 38 and 41 teached by Mme FAVRET from the Department of Computer Science**

#################
#French Version #
#################
```{r}
#Figure of the Learning Sequences of the Modules 35, 38 and 41 teached by Mme FAVRET from the Department of Computer Science

#Define the name of the file
fig_Sequences_35_38_41 = paste("Sequences-Modules_35_38_41-Teacher_FAVRET-Dep_ComputerScience", sep = "")

#Set the Figure file name and Figure size, margins and positions of the graphs
png(paste("../Figures/Vrs_Français/", fig_Sequences_35_38_41, ".png", sep = ""), heigh = 750, width = 1400)
layout(matrix(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4), ncol=6, byrow=TRUE))
par(mar=c(8,9,3,5)+0.1, oma=c(0,1,9,1))
par(family="serif")

#Define the title of the Figure
title_fig_Sequences_35_38_41 = paste("Séquences Pédagogiques de 2013 à 2020 pour les Cours N°35, N°38 et N°41 \n enseignés par Mme FAVRET du Département d'Informatique", sep = "")

#Plot the Seqplot of the Module 35 and Define its axis and labels
seqplot(mvad.Sequences_35, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_35)),
        cpal = seqplot_color_35, space = 0.15, main = "")
title(main=list("Séquences du Cours N°35 intitulé «Base de Numérotation»",  cex = 2.8, font = 1))
axis(1, at = 0.5:(max(prep_Sequences_35$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_35$Resources_Rank), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_35$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang des Ressources dans les Séquences Pédagogiques", cex.lab = 2.8, line = 5)
title(ylab = "Années", cex.lab = 2.8, line = 7)

#Plot the Seqplot of the Module 38 and Define its axis and labels
seqplot(mvad.Sequences_38, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_38)),
        cpal = seqplot_color_38, space = 0.15, main = "")
title(main=list("Séquences du Cours N°38 intitulé «Informatique Appliquée»",  cex = 2.8, font = 1))
axis(1, at = 0.5:(max(prep_Sequences_38$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_38$Resources_Rank), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_38$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang des Ressources dans les Séquences Pédagogiques", cex.lab = 2.8, line = 5)
title(ylab = "Années", cex.lab = 2.8, line = 7)

#Plot the Seqplot of the Module 41 and Define its axis and labels
seqplot(mvad.Sequences_41, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_41)),
        cpal = seqplot_color_41, space = 0.15, main = "")
title(main=list("Séquences du Cours N°41 intitulé «Introduction à la Programmation»",  cex = 2.8, font = 1))
axis(1, at = 0.5:(max(prep_Sequences_41$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_41$Resources_Rank), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_41$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang des Ressources dans les Séquences Pédagogiques", cex.lab = 2.8, line = 5)
title(ylab = "Années", cex.lab = 2.8, line = 7)

#Plot the Seqlegend of the Sequences and Define its title
seqlegend(seqdef(legend_order_FR), cpal = legend_color, ltext = legend_order_FR, cex = 2.8, position = 'center')
text(1, 1, paste("Type des Ressources"), cex = 2.8)

#Put the main Title of the Figure
mtext(title_fig_Sequences_35_38_41, outer=TRUE,  cex=2.3, font = 1, line=2)

#Save the Figure
dev.off()
```

##################
#English Version #
##################
```{r}
#Figure of the Learning Sequences of the Modules 35, 38 and 41 teached by Mme FAVRET from the Department of Computer Science

#Define the name of the file
fig_Sequences_35_38_41 = paste("Sequences-Modules_35_38_41-Teacher_FAVRET-Dep_ComputerScience", sep = "")

#Set the Figure file name and Figure size, margins and positions of the graphs
png(paste("../Figures/Vrs_English/", fig_Sequences_35_38_41, ".png", sep = ""), heigh = 700, width = 1400)
layout(matrix(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 3, 4, 4), ncol=6, byrow=TRUE))
par(mar=c(8,9,3,5)+0.1, oma=c(0,1,8,1))

#Define the title of the Figure
title_fig_Sequences_35_38_41 = paste("Learning Sequences from 2013 to 2020, \n for the Modules «35», «38» et «41» teached by Mme FAVRET from the Department of Computer Science", sep = "")

#Plot the Seqplot of the Module 35 and Define its axis and labels
seqplot(mvad.Sequences_35, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_35)),
        cpal = seqplot_color_35, space = 0.15, main = "")
title(main=list("Learning Sequences for the Module «35»",  cex = 2.5, font = 3))
axis(1, at = 0.5:(max(prep_Sequences_35$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_35$Resources_Rank), sep = ""), cex.axis = 2.3, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_35$Year, sep = ""), las = 1,  cex.axis = 2.3, line = 0, tick = FALSE)
title(xlab = "Rank of the Resources in the Learning Sequences", cex.lab = 2.5, line = 5)
title(ylab = "Years", cex.lab = 2.5, line = 7)

#Plot the Seqplot of the Module 38 and Define its axis and labels
seqplot(mvad.Sequences_38, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_38)),
        cpal = seqplot_color_38, space = 0.15, main = "")
title(main=list("Learning Sequences for the Module «38»",  cex = 2.5, font = 3))
axis(1, at = 0.5:(max(prep_Sequences_38$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_38$Resources_Rank), sep = ""), cex.axis = 2.3, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_38$Year, sep = ""), las = 1,  cex.axis = 2.3, line = 0, tick = FALSE)
title(xlab = "Rank of the Resources in the Learning Sequences", cex.lab = 2.5, line = 5)
title(ylab = "Years", cex.lab = 2.5, line = 7)

#Plot the Seqplot of the Module 41 and Define its axis and labels
seqplot(mvad.Sequences_41, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_41)),
        cpal = seqplot_color_41, space = 0.15, main = "")
title(main=list("Learning Sequences for the Module «41»",  cex = 2.5, font = 3))
axis(1, at = 0.5:(max(prep_Sequences_41$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_41$Resources_Rank), sep = ""), cex.axis = 2.3, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_41$Year, sep = ""), las = 1,  cex.axis = 2.3, line = 0, tick = FALSE)
title(xlab = "Rank of the Resources in the Learning Sequences", cex.lab = 2.5, line = 5)
title(ylab = "Years", cex.lab = 2.5, line = 7)

#Plot the Seqlegend of the Sequences and Define its title
seqlegend(seqdef(legend_order_EN), cpal = legend_color, ltext = legend_order_EN, cex = 2.5, position = 'center')
text(1, 1, paste("Type of Resources"), cex = 2.5)

#Put the main Title of the Figure
mtext(title_fig_Sequences_35_38_41, outer=TRUE,  cex=2, font = 1, line=2)

#Save the Figure
dev.off()
```


**Learning Sequences of the Modules 11, 41 and 80 respectively teached by Mme GALLE, Mme FAVRET and Mr AMIRAULT from the Department of Computer Science**

#################
#French Version #
#################
```{r}
#Figure of the Learning Sequences of the Modules 11, 41 and 80 respectively teached by Mme GALLE, Mme FAVRET and Mr AMIRAULT from the Department of Computer Science

#Define the name of the file
fig_Sequences_11_41_80 = paste("Sequences-Modules_11_41_80-Teacher_rspvly_GALLE_FAVRET_AMIRAULT-Dep_ComputerScience", sep = "")

#Set the Figure file name and Figure size, margins and positions of the graphs
png(paste("../Figures/Vrs_Français/", fig_Sequences_11_41_80, ".png", sep = ""), heigh = 750, width = 1500)
layout(matrix(c(1, 1, 2, 2, 3, 3, 4, 4), ncol=4, byrow=TRUE))
par(mar=c(8,9,3,5)+0.1, oma=c(0,1,9,1))
par(family="serif")

#Define the title of the Figure
title_fig_Sequences_11_41_80 = paste("Séquences Pédagogiques de 2013 à 2020 pour les Cours «11», «41» et «80» \n enseignés respectivement par Mme GALLE, Mme FAVRET et Mr AMIRAULT du Département d'Informatique", sep = "")

#Plot the Seqplot of the Module 11 and Define its axis and labels
seqplot(mvad.Sequences_11, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_11)),
        cpal = seqplot_color_11, space = 0.15, main = "")
title(main=list("Séquences du Cours N°11 intitulé «Informatique Industrielle»",  cex = 2.8, font = 1))
axis(1, at = 0.5:(max(prep_Sequences_11$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_11$Resources_Rank), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_11$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang des Ressources dans les Séquences Pédagogiques", cex.lab = 2.8, line = 5)
title(ylab = "Années", cex.lab = 2.8, line = 7)

#Plot the Seqplot of the Module 41 and Define its axis and labels
seqplot(mvad.Sequences_41, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_41)),
        cpal = seqplot_color_41, space = 0.15, main = "")
title(main=list("Séquences du Cours N°41 intitulé «Introduction à la Programmation»",  cex = 2.8, font = 1))
axis(1, at = 0.5:(max(prep_Sequences_41$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_41$Resources_Rank), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_41$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang des Ressources dans les Séquences Pédagogiques", cex.lab = 2.8, line = 5)
title(ylab = "Années", cex.lab = 2.8, line = 7)

#Plot the Seqplot of the Module 80 and Define its axis and labels
seqplot(mvad.Sequences_80, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_80)),
        cpal = seqplot_color_80, space = 0.15, main = "")
title(main=list("Séquences du Cours N°80 intitulé «Informatique de Gestion»",  cex = 2.8, font = 1))
axis(1, at = 0.5:(max(prep_Sequences_80$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_80$Resources_Rank), sep = ""), cex.axis = 2.5, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_80$Year, sep = ""), las = 1,  cex.axis = 2.5, line = 0, tick = FALSE)
title(xlab = "Rang des Ressources dans les Séquences Pédagogiques", cex.lab = 2.8, line = 5)
title(ylab = "Années", cex.lab = 2.8, line = 7)

#Plot the Seqlegend of the Sequences and Define its title
seqlegend(seqdef(legend_order_FR), cpal = legend_color, ltext = legend_order_FR, cex = 2.8, position = 'center')
text(1, 1, paste("Type des Ressources"), cex = 2.8)

#Put the main Title of the Figure
mtext(title_fig_Sequences_11_41_80, outer=TRUE,  cex=2.3, font = 1, line=2)

#Save the Figure
dev.off()
```

##################
#English Version #
##################
```{r}
#Figure of the Learning Sequences of the Modules 11, 41 and 80 respectively teached by Mme GALLE, Mme FAVRET and Mr AMIRAULT from the Department of Computer Science

#Define the name of the file
fig_Sequences_11_41_80 = paste("Sequences-Modules_11_41_80-Teacher_rspvly_GALLE_FAVRET_AMIRAULT-Dep_ComputerScience", sep = "")

#Set the Figure file name and Figure size, margins and positions of the graphs
png(paste("../Figures/Vrs_English/", fig_Sequences_11_41_80, ".png", sep = ""), heigh = 750, width = 1500)
layout(matrix(c(1, 1, 2, 2, 3, 3, 4, 4), ncol=4, byrow=TRUE))
par(mar=c(8,9,3,5)+0.1, oma=c(0,1,8,1))

#Define the title of the Figure
title_fig_Sequences_11_41_80 = paste("Learning Sequences from 2013 to 2020 for the Modules «11», «41» and «80», \n respectively teached by Mme GALLE, Mme FAVRET and Mr AMIRAULT from the Department of Computer Science", sep = "")

#Plot the Seqplot of the Module 11 and Define its axis and labels
seqplot(mvad.Sequences_11, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_11)),
        cpal = seqplot_color_11, space = 0.15, main = "")
title(main=list("Learning Sequences for the Module «11» teached by Mme GALLE ",  cex = 2.3, font = 3))
axis(1, at = 0.5:(max(prep_Sequences_11$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_11$Resources_Rank), sep = ""), cex.axis = 2.2, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_11$Year, sep = ""), las = 1,  cex.axis = 2.2, line = 0, tick = FALSE)
title(xlab = "Rank of the Ressources in the Learning Sequences", cex.lab = 2.5, line = 5)
title(ylab = "Years", cex.lab = 2.5, line = 7)

#Plot the Seqplot of the Module 41 and Define its axis and labels
seqplot(mvad.Sequences_41, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_41)),
        cpal = seqplot_color_41, space = 0.15, main = "")
title(main=list("Learning Sequences for the Module «41» teached by Mme FAVRET ",  cex = 2.3, font = 3))
axis(1, at = 0.5:(max(prep_Sequences_41$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_41$Resources_Rank), sep = ""), cex.axis = 2.2, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_41$Year, sep = ""), las = 1,  cex.axis = 2.2, line = 0, tick = FALSE)
title(xlab = "Rank of the Ressources in the Learning Sequences", cex.lab = 2.5, line = 5)
title(ylab = "Years", cex.lab = 2.5, line = 7)

#Plot the Seqplot of the Module 80 and Define its axis and labels
seqplot(mvad.Sequences_80, with.legend = FALSE, axes = FALSE, ann = FALSE, ytlab = rep("", nrow(seq_Sequences_80)),
        cpal = seqplot_color_80, space = 0.15, main = "")
title(main=list("Learning Sequences for the Module «80» teached by Mr AMIRAULT ",  cex = 2.3, font = 3))
axis(1, at = 0.5:(max(prep_Sequences_80$Resources_Rank)-0.5), labels = paste(unique(prep_Sequences_80$Resources_Rank), sep = ""), cex.axis = 2.2, line = 0, tick = TRUE, padj = 0.5)
axis(2, at = c(0.65, 1.80, 2.95, 4.1, 5.25, 6.40, 7.55, 8.70), labels = paste(seq_Sequences_80$Year, sep = ""), las = 1,  cex.axis = 2.2, line = 0, tick = FALSE)
title(xlab = "Rank of the Ressources in the Learning Sequences", cex.lab = 2.5, line = 5)
title(ylab = "Years", cex.lab = 2.5, line = 7)

#Plot the Seqlegend of the Sequences and Define its title
seqlegend(seqdef(legend_order_EN), cpal = legend_color, ltext = legend_order_EN, cex = 2.5, position = 'center')
text(1, 1, paste("Type of Ressources"), cex = 2.5)

#Put the main Title of the Figure
mtext(title_fig_Sequences_11_41_80, outer=TRUE,  cex=2, font = 1, line=2)

#Save the Figure
dev.off()
```
